Graph Topology Learning from Binary Signals on Graph

### 2022-04-27 poster html copy/poster html.Rmd
poster update.

```{r GTG, echo=FALSE,out.width="90%", out.height="20%",fig.cap="Circular Embedding of ground truth graph",fig.show='hold',fig.align='center'}
knitr::include_graphics(c("pictures/gt_graph.png"))
```

@@

<hr /> 
<hr /> 
$\textbf{Algorithm 1:}$ Estimate $A$ given $Y$.
<hr /> 
<hr />

@@

To generate a single signal for a given adjacency matrix $A \in \mathbb{R}^{N\times N}$ and latent factor vector $h \in \mathbb{R}^N$ (each $h_i \sim \mathcal{N}(0,1)$), a vector of odds, $Ah$, is compared to a vector $T$, where $T_i$ selected uniformly at random for each $i = 1, \ldots , N$. If $T_k < Ah_k$, then node $k$ takes the signal value of $1$, and $0$ otherwise. We generate $M = 100$ synthetic signals, and use them to learn an adjacency matrix. The learned graph is found with parameter values $\alpha = .2$, $a = 1$ and $b = -1$.

Heat maps of the ground truth adjacency matrix and estimated adjacency matrix are given in Figure 2, along with circular embedding of the ground truth and estimated graphs in Figure 3.

@@

```{r EAG, echo=FALSE,out.width="90%", out.height="20%",fig.cap="Circular Embedding of Estimated graph",fig.show='hold',fig.align='center'}
knitr::include_graphics(c("pictures/est_graph.png"))
```

# Discussion

Currently, GSP frameworks such as ours have limitations. For instance, these frameworks require the input to be set of complete signals. This limits the size of graphs that can be learned. Another related limitation, is the scalability of the algorithms used to learn a topology for the graph. In @saboksayr2021accelerated the author shows fast proximal-gradient iterations can be applied to the framework given by @kalofolias2016learn converges to a globally optimal solution in $O (1/k)$. A natural next step would be to apply fast proximal-gradient iterations our framework to overcome scalability issues.

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```
# Acknowledgement
This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises. This work would not have been possible without the guidence of Dr. Jing Guo. I am extremely grateful for all of meetings over the semester.

>>>>

```{r GTG, echo=FALSE,out.width="80%", out.height="20%",fig.cap="Circular Embedding of ground truth graph",fig.show='hold',fig.align='center'}
knitr::include_graphics(c("pictures/gt_graph.png"))
```

@@

$\textbf{Algorithm 1:}$ Estimate $A$ given $Y$.

@@

To generate a single signal for a given adjacency matrix $A \in \mathbb{R}^{N\times N}$ and latent factor vector $h \in \mathbb{R}^N$ (each $h_i \sim \mathcal{N}(0,1)$), a vector of odds, $Ah$, is compared to a vector $T$, where $T_i$ selected uniformly at random for each $i = 1, \ldots , N$. If $T_k < Ah_k$, then node $k$ takes the signal value of $1$, and $0$ otherwise. We generate $M = 100$ synthetic signals, and use them to learn an adjacency matrix. The learned graph is found with parameter values $\alpha = .2$, $a = 1$ and $b = -1$. Heat maps of the ground truth adjacency matrix and estimated adjacency matrix are given in Figure 2, along with circular embedding of the ground truth and estimated graphs in Figure 3.

@@

```{r EAG, echo=FALSE,out.width="80%", out.height="20%",fig.cap="Circular Embedding of Estimated graph",fig.show='hold',fig.align='center'}
knitr::include_graphics(c("pictures/est_graph.png"))
``` 
# Discussion
One shortcoming of this framework is it requires the input to be a complete set of signals. This limits the size of graphs that can be learned. Another, is the scalability of the algorithms used to learn a topology for the graph. In @saboksayr2021accelerated the author shows fast proximal-gradient iterations can be applied to the framework given by @kalofolias2016learn converges to a globally optimal solution in $O (1/k)$. A natural next step would be to apply fast proximal-gradient iterations our framework to overcome scalability issues.

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```
# Acknowledgement
This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises. Thank you Dr. Robin Donatello for approving this project. This work would not have been possible without the guidence of Dr. Jing Guo. I am extremely grateful for all of meetings over the semester.
